---
title: "Homework 5"
author: "Fangyi Chen"
date: '`r format(Sys.time(), "%Y-%m-%d")`'
output: github_document
---


```{r load_libraries}
library(tidyverse)
library(ggridges)
library(rvest)
library(broom)

```



## Problem 2
```{r data loading & preprocessing}
file_names = list.files("data")

combined_df = map_df(file_names, ~{
  df = read_csv(file.path("data", .x), show_col_types = FALSE)
  
  subject_id = str_extract(.x, "\\d+")
  
  arm = str_extract(.x, "(con|exp)")
  
  df |> 
    mutate(subject_id = subject_id,
           arm = arm) |> 
    select(subject_id, arm, everything())
  
})

```


```{r spaghetti plot}

combined_df |> 
      pivot_longer(week_1:week_8,
                 names_to = "week",
                 names_prefix = "week_" ,
                 values_to = "observation") |> 
  ggplot(aes(x=week,y= observation, group=subject_id, color=arm)) +
  geom_line() + 
  facet_grid(. ~arm) +
  labs(title = "Spaghetti Plot of Observations Over Time",
       x = "Week",
       y = "Observation") 

```
### Comments: In the experiment arm , we did perceive a increasing trend from week 1 to week8, whereas for control group, there appears to have difference between week1 and week8 in the end. 

## Problem 3

```{r write and execute function}
set.seed(1)

list_mu = c (0, 1, 2, 3, 4, 5, 6)

gather_test_results = function(mu) {

  n = 30
  sigma = 5
  
  simulated_data =rnorm(n=n, mean=mu, sd=sigma)
  test_results = tibble(tidy(t.test(simulated_data, mu=0)))
  
  
  return (tibble(
    true_mean = mu,
    p_value = test_results$p.value,
    estimated_mu = test_results$estimate
    
  ))
}

sim_results_df = 
  expand_grid(
    true_mu = list_mu,
    no_sample = 1:5000
  ) |> 
  mutate(
    estimate_df = map(true_mu, gather_test_results)
  ) |> 
  unnest(estimate_df)

```


```{r plot effect size and power}
alpha = 0.05
sim_results_df |> 
  group_by(true_mu) |> 
  summarise(power = mean(p_value < alpha),
            avg_estimate  = mean(estimated_mu)) |> 
  ggplot(aes(x=true_mu, y = power)) +
  geom_line() +
  labs(title = "Effect Size and Power",
       x = "True Value of mean",
       y = "Power") 

```
## As shown on plot, when we increase the effect size (difference between the true population mean and null hypothesis mean), we perceive a higher power of the statistical test. On the contrary, as we decreases the effect size, lower power or smaller statistical difference can be found.


```{r}
sim_results_df |> 
  filter(p_value < alpha) |> 
  group_by(true_mu) |> 
  summarise(avg_estimate_reject  = mean(estimated_mu)) |> 
  ggplot(aes(x=true_mu, y = avg_estimate_reject)) +
  geom_line() +
  labs(title = "Estimated mu in Rejected and True Value of mu",
       x = "True Value of mean",
       y = "Average estimate mu (rejected)") 
```




